Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-07-23 exp1/iswc2013.tex
Introductory material
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@610 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

First, note that the concept of parameters as considered in the
introduction is known as \emph{factors} in DoE. For each factor, we
have chosen in this paper to only deal with the relatively
straightforward aspects of the DoE formalism, and therefore constrain
the experiment strictly to 2 levels.

>>>>

\subsection{Design of Experiments Concepts}

We expect DoE to be new to most readers, but some familiarity with
hypothesis testing is assumed.

First, note that the concept of parameters as considered above is
known as \emph{factors} in DoE. For each factor, one may make a
measurement of a \emph{response variable} at certain \emph{levels},
e.g. one may measure the response time of a SPARQL endpoint by
measuring it when it contains 1 or 2 million triples. Then, the
response time is the response variable, the factor is the number of
triples and there are two levels, 1 or 2 million triples. We have chosen in
this paper to only deal with the relatively straightforward aspects of
the DoE formalism, and therefore constrain the experiment strictly to
2 levels.

% TODO: 
% 1) what are effects
%% 2) what are levels
%% 3) what are factors 
%% 4) Can run 2^8 experiments, call full factorial
%% 5) What are normal plots
%% 6) explain interaction effects

@@
